\LARGE \textbf{Constrained Geometric Attitude Control on \( \SO \)}

### 2017-01-05 manuscript.tex
Update domain for control proof
Update stability proof with quadratic function domain

\begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
Consider a domain \( D \) about the desired attitude defined as
\begin{align}
	D = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
\end{align}
Then the following statements hold:
\begin{enumerate}[(i)]
	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
	\begin{gather}
		\norm{A} < b_2 \norm{e_{R_A}}^2 = c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
	\end{gather}
  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
  \begin{align*}
    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
  \end{align*}
	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
	\begin{gather}
		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
	\end{gather}
	\item Upper bounds of the attitude error vectors \( e_{R_A} \) and \( e_{R_B} \) are given by
	\begin{gather}
		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
	\end{gather}

@@

\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for the estimated uncertainty \( \bar{\Delta} \) as follows:
\begin{align}
	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} , \label{eqn:adaptive_control} \\
	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} . \label{eqn:delta_dot}
\end{align}
If \( c \) is chosen such that
\begin{gather}
	0 < c < \min \braces{\sqrt{\frac{2 k_R b_1}{\lambda_m}},\sqrt{\frac{2 k_R b_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
\end{gather}
  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
\end{prop}
\begin{proof}
See~\Cref{proof:adaptive_control}
\end{proof}

@@

\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
Consider the Lyapunov function \( \mathcal{V} \) given by
\begin{align*}
	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
\end{align*}
over the domain \( D \) in~\cref{eqn:domain}.
From~\Cref{prop:eR_dot_bound,prop:config_error}, the configuration error function is bounded in \( D \) by
\begin{align*}
    b_1 \norm{e_{R_A}}^2 < b_1 \norm{e_{R}}^2 < \Psi < b_2 \norm{e_{R_A}}^2 < b_2 \norm{e_{R}}^2 .
\end{align*}
Using this the Lyapunov function \( \mathcal{V} \) is bounded by
\begin{align*} %\label{eqn:v_upper_bound}
	z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
\end{align*}
where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
\begin{align*}
	W_1 & = \begin{bmatrix}
		k_R b_1 & \frac{1}{2} c \lambda_m & 0 \\
		\frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
		0 & 0 & \frac{1}{2 k_\Delta}
	\end{bmatrix},\\
	W_2 & = \begin{bmatrix}
		k_R b_2 & \frac{1}{2} c \lambda_M & 0 \\
		\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
		0 & 0 & \frac{1}{2 k_\Delta}
	\end{bmatrix} .
\end{align*}
The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
\begin{align}
	\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
	&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
\end{align}
where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
\begin{align*}
	 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
\end{align*}
Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
\begin{gather*}
	\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
\end{gather*}
where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
\begin{gather*}
	M = \begin{bmatrix}
		k_R c & \frac{k_\Omega c}{2} \\
		\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
	\end{bmatrix} .
\end{gather*}
If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D$. As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded. Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.

>>>>

\begin{prop}[Bound on \( \bm{\dot{e}_R} \)]\label{prop:eR_dot_bound}
Consider a domain \( D \) about the desired attitude defined as
\begin{align}
	D_2 = \braces{R \in \SO \vert \Psi < \psi < h_1, r^T R^T v < \beta < \cos \theta}. \label{eqn:domain}
\end{align}
Then the following statements hold:
\begin{enumerate}[(i)]
	\item \label{item:prop_eR_dot_bound_AB} Upper bounds of \( A(R) \) and \( B(R) \) are given by
	\begin{gather}
		\norm{A} < b_2 \norm{e_{R_A}}^2 < c_A  , \quad \norm{B} < c_B . \label{eqn:AB_bound}
	\end{gather}
  where the constant \( b_2\) is given by \( b_2 = \frac{h_1 h_4}{h_5 \parenth{h_1 - \psi}}\) for
  \begin{align*}
    h_4 &= \min\braces{g_1 + g_2, g_2 + g_3 , g_3 + g_1} ,\\
    h_5 &= \min\braces{\parenth{g_1 + g_2}^2,\parenth{g_2 + g_3}^2 , \parenth{g_3 + g_1}^2} .\\
  \end{align*}
	\item \label{item:prop_eR_dot_bound_EF} Upper bounds of \( E(R,R_d) \) and \( F(R) \) are given by
	\begin{gather}
		\norm{E} \leq \frac{1}{\sqrt{2}} \tr{G}  , \label{eqn:E_bound} \\
		\norm{F} \leq \frac{\parenth{\beta^2 + 1}\parenth{\beta - \cos \theta}^2 + 1 + \beta^2 \parenth{\beta^2-2}}{\alpha^2 \parenth{\beta-\cos \theta}^4} . \label{eqn:F_bound}
	\end{gather}
	\item Upper bounds of the attitude error vectors \( e_{R_A} \) and \( e_{R_B} \) are given by
	\begin{gather}
		\norm{e_{R_A}} \leq \sqrt{\frac{\psi}{b_1}}, \label{eqn:eRA_bound} \\
		\norm{e_{R_B}} \leq \frac{\sin\theta}{\alpha \parenth{\cos \theta - \beta}}. \label{eqn:eRB_bound}
	\end{gather}

@@

\begin{prop}[Adaptive Attitude Control]\label{prop:adaptive_control}
Given  a desired attitude command \( (R_d, \Omega_d = 0 )\) and positive constants \( k_R, k_\Omega, k_\Delta, c \in \R \), we define a control input \( u \in \R^3\) and an adaptive update law for the estimated uncertainty \( \bar{\Delta} \) as follows:
\begin{align}
	u &= - k_R e_R - k_\Omega e_\Omega + \Omega \times J \Omega - W \bar{\Delta} , \label{eqn:adaptive_control} \\
	\dot{\bar{\Delta}} &= k_\Delta W^T \parenth{e_\Omega + c e_R} . \label{eqn:delta_dot}
\end{align}
If \( c \) is chosen such that
\begin{gather}
	0 < c < \min \braces{\sqrt{\frac{2 k_R n_1}{\lambda_m}},\sqrt{\frac{2 k_R n_2}{\lambda_M}}, \frac{4 k_R k_\Omega}{k_\Omega^2 + 4 k_R \lambda_M H}} , \label{eqn:c_bound}
\end{gather}
  the zero equilibrium of the error vectors is stable in the sense of Lyapunov. Furthermore, $e_R,e_\Omega\rightarrow 0$ as $t\rightarrow\infty$, and $\bar\Delta$ is  bounded.
\end{prop}
\begin{proof}
See~\Cref{proof:adaptive_control}
\end{proof}

@@

\subsection{Proof of~\Cref{prop:adaptive_control}}\label{proof:adaptive_control}
Consider the Lyapunov function \( \mathcal{V} \) given by
\begin{align*}
	\mathcal{V} = \frac{1}{2} e_\Omega \cdot J e_\Omega + k_R \Psi + c J e_\Omega \cdot e_R + \frac{1}{2 k_\Delta} e_\Delta \cdot e_\Delta , %\label{eqn:v_adapt}
\end{align*}
over the domain \( D_3 = D_1 \cup D_2\), which ensures that the properties of~\Cref{prop:config_error,prop:error_dyn} are satisfied.

From~\Cref{prop:config_error}, the configuration error function is locally quadratic and it is bounded in \( D_3 \) by
\begin{align*}
    n_1 \norm{e_R} < \Psi <  n_2 \norm{e_{R}}^2 ,
\end{align*}
for constants \( 0 < n_1 \leq n_2 \)~\cite[Definition 6.28]{bullo2004}.
Using this the Lyapunov function \( \mathcal{V} \) is bounded by
\begin{align*} %\label{eqn:v_upper_bound}
	z^T W_1 z \leq \mathcal{V} \leq z^T W_2 z ,
\end{align*}
where \( e_\Delta = \Delta - \bar{\Delta} \), \( z = [\|e_R\|,\|e_\Omega\|,\|e_\Delta\|]^T\in\R^3 \) and the matrices \(W_1,W_2 \in \R^{3 \times 3}\) are given by
\begin{align*}
	W_1 & = \begin{bmatrix}
		k_R n_1 & \frac{1}{2} c \lambda_m & 0 \\
		\frac{1}{2} c \lambda_m & \frac{1}{2} \lambda_m & 0 \\
		0 & 0 & \frac{1}{2 k_\Delta}
	\end{bmatrix},\\
	W_2 & = \begin{bmatrix}
		k_R n_2 & \frac{1}{2} c \lambda_M & 0 \\
		\frac{1}{2} c \lambda_M & \frac{1}{2} \lambda_M & 0 \\
		0 & 0 & \frac{1}{2 k_\Delta}
	\end{bmatrix} .
\end{align*}
The time derivative of \( \mathcal{V}\) with the control input defined by~\cref{eqn:adaptive_control} is given as
\begin{align}
	\dot{\mathcal{V}} =& - k_\Omega e_\Omega^T e_\Omega + \parenth{e_\Omega + c e_R}^T W e_\Delta - k_R c e_R^T e_R \nonumber\\
	&- k_\Omega c e_R^T e_\Omega + c J e_\Omega^T \dot{e}_R - \frac{1}{k_\Delta} e_\Delta^T \dot{\bar{\Delta}} , \label{eqn:vdot}
\end{align}
where we used \( \dot{e}_\Delta = - \dot{\bar{\Delta}} \).
The terms linearly dependent on \( e_\Delta\) are combined with~\cref{eqn:delta_dot} to yield
\begin{align*}
	 e_\Delta^T \parenth{W^T \parenth{e_\Omega + c e_R} - \frac{1}{k_\Delta} \dot{\bar{\Delta}}} = 0 . 
\end{align*}
Using~\Cref{prop:eR_dot_bound} an upper bound on \( \dot{\mathcal{V}} \) is written as
\begin{gather*}
	\dot{\mathcal{V}} \leq -\zeta^T M \zeta ,
\end{gather*}
where $\zeta=[\|e_R\|,\|e_\Omega\|]\in\R^2$, and the matrix \( M \in \R^{2 \times 2} \) is 
\begin{gather*}
	M = \begin{bmatrix}
		k_R c & \frac{k_\Omega c}{2} \\
		\frac{k_\Omega c}{2} & k_\Omega - c \lambda_M H
	\end{bmatrix} .
\end{gather*}
If \( c \) is chosen such that~\cref{eqn:c_bound} is satisfied then the matrices \( W_1, W_2 \) and \( M \) are positive definite.
This implies that $\mathcal{V}$ is positive definite and decrescent, and $\dot{\mathcal{V}}$ is negative semidefinite in the domain $D_3$. As such, the zero equilibrium is stable in the sense of Lyapunov, and all of the error variables are bounded. Furthermore, $\lim_{t\to\infty} \zeta=0$ according to the LaShalle-Yoshizawa theorem~\cite{khalil1996}.
